POMDP comparisons across sigma_m, sigma_g

### 2018-01-26 appendix/appendixB.Rmd
plotting

---
output: github_document
---

@@

```{r plotting}
library(gridExtra)
library(ggthemes)
library(ggplot2)
library(Cairo)
library(extrafont)
library(hrbrthemes)

extrafont::loadfonts()
knitr::opts_chunk$set( dev="cairo_pdf")
hrbrthemes::import_roboto_condensed() 
ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())

palette <- ptol_pal()(6)
palette <- c("#D9661F", "#3B7EA1",  "#6C3302", "#FDB515", "#00B0DA",  "#CFDD45") # berkeley colors

colors <- set_names(c(palette[c(1:4,2,5)], "grey", "black"), 
                    c("TAC", "POMDP", "MSY", "CE", 
                      "POMDP: low prior",
                      "POMDP: medium prior",
                      "biomass",
                      "catch"))
```

```{r libraries, message=FALSE}
# devtools::install_github("boettiger-lab/sarsop")  ## install package first if necessary.
library(tidyverse)
library(sarsop)
library(nimble)
library(parallel)
```

@@

```{r}
sims %>%
  filter(model %in% c("biomass", "catch", "POMDP", "Reed", "pgy")) %>%
  ggplot(aes(year, stock, col=model)) +
  geom_line(lwd=1) +
  scale_color_manual(values = c("black", "grey", "#D9661F", "#3B7EA1", "#FDB515", "#6C3302",  "#00B0DA",  "#CFDD45")) +
  facet_wrap(~commonname, scales = "free", ncol=1) + theme_bw()  
```

>>>>

---
output: pdf_document
---

@@

```{r libraries, message=FALSE}
# devtools::install_github("boettiger-lab/sarsop")  ## install package first if necessary.
library(tidyverse)
library(sarsop)
library(nimble)
library(parallel)
library(gridExtra)
```

```{r plotting}
## This chunk is optional, just tweaks plot appearance / fonts
library(ggthemes)
library(Cairo)
library(extrafont)
library(hrbrthemes)

extrafont::loadfonts()
knitr::opts_chunk$set( dev="cairo_pdf")
hrbrthemes::import_roboto_condensed() 
ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())
#palette <- ptol_pal()(6)
```

```{r}
palette <- c("#D9661F", "#3B7EA1",  "#6C3302", "#FDB515", "#00B0DA",  "#CFDD45") # berkeley colors
colors <- set_names(c(palette[c(1:4,2,5)], "grey", "black"), 
                    c("TAC", "POMDP", "MSY", "CE", 
                      "POMDP: low prior",
                      "POMDP: medium prior",
                      "biomass",
                      "catch"))
```

@@

```{r}
ram_ex <- read_csv(file.path(log_dir, "ram_ex.csv"))

ram_ex %>%
  filter(model %in% c("biomass", "catch", "POMDP", "Reed", "pgy", "msy")) %>%
   mutate(model = fct_recode(model,
                             "MSY" = "msy",
                             "CE" = "Reed",
                             "TAC" = "pgy"
                             )) %>%
  ggplot(aes(year, stock, col=model)) +
  geom_line(lwd=1) +
  scale_color_manual(values = colors) +
  facet_wrap(~commonname, scales = "free", ncol=1)  
```

### 2018-01-26 appendix/appendix_harvestfirst.Rmd
plotting

```{r aethetics, include=FALSE}
knitr::opts_chunk$set(comment="", message=FALSE, cache=TRUE)
ggplot2::theme_set(ggplot2::theme_bw())
```

```{r message=FALSE}
# devtools::install_github("boettiger-lab/sarsop")  ## install package first if necessary.
library(sarsop)       # the main POMDP package
library(tidyverse)    # for munging and plotting
library(parallel)
```

```{r plotting}
library(gridExtra)
library(ggthemes)
library(ggplot2)
library(Cairo)
library(extrafont)
library(hrbrthemes)

extrafont::loadfonts()
knitr::opts_chunk$set( dev="cairo_pdf")
hrbrthemes::import_roboto_condensed() 
ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())

palette <- ptol_pal()(6)
palette <- c("#D9661F", "#3B7EA1",  "#6C3302", "#FDB515", "#00B0DA",  "#CFDD45") # berkeley colors

@@

```{r pomdp_sims}
set.seed(12345)
true <- 3 # sigma_g = 0.15, sigma_m = 0
source("../appendix/pomdp_overestimate.R")
pomdp_overest_sims <- 
  map2_dfr(models, alphas, function(.x, .y){
    pomdp_overestimates(transition = .x$transition, 
            model_observation = .x$observation, 
            reward = .x$reward, 
            discount = discount, 
            true_observation = models[[true]]$observation,
            x0 = x0,
            Tmax = Tmax,
            alpha = .y,
            reps = reps)$df %>% 
              mutate(method = "pomdp") # include a column labeling method
           },
           .id = "scenario"
  )
```

@@

```{r  fig.width=5, fig.height=7, fig.cap=""}
prior <- 
  ggplot(priors,aes(state, belief, color = policy)) + 
  geom_line(lwd=1)  + 
  scale_color_manual(values = colors) +
  coord_cartesian(xlim = c(0,1)) +
  ggtitle("POMDP priors") + 
  xlab("Estimated stock biomass") + 
  theme(legend.position = "none")

harvest <- policy_df %>%
  ggplot(aes(state, harvest, col=policy)) + 
  geom_line(lwd=1)  +
  scale_color_manual(values = colors) +
  coord_cartesian(xlim = c(0,1), ylim = c(0, .8)) + 
  ggtitle("Harvest view") + 
  theme(legend.position="none") + 
  xlab("Estimated stock biomass")

escapement <- policy_df %>%
  ggplot(aes(state, escapement, col=policy)) + 
  geom_line(lwd=1)  +
  scale_color_manual(values = colors) +
  coord_cartesian(xlim = c(0,1), ylim = c(0, .8)) +
  xlab("Estimated stock biomass") +
  ggtitle("Escapement view") + 
  theme(legend.position = "bottom")

gridExtra::grid.arrange(harvest, escapement, prior,
  layout_matrix = rbind(1,1,2,2, 3))

>>>>

```{r aethetics, include=FALSE}
knitr::opts_chunk$set(comment="", message=FALSE, cache=TRUE)
```

```{r library, message=FALSE}
# devtools::install_github("boettiger-lab/sarsop")  ## install package first if necessary.
library(sarsop)       # the main POMDP package
library(tidyverse)    # for munging and plotting
library(parallel)
library(gridExtra)
```

```{r optional_plotting_config}
library(ggthemes)
library(ggplot2)
library(Cairo)
library(extrafont)
library(hrbrthemes)

extrafont::loadfonts()
knitr::opts_chunk$set( dev="cairo_pdf")
hrbrthemes::import_roboto_condensed() 
ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())
```

```{r colors}
#palette <- ptol_pal()(6)
palette <- c("#D9661F", "#3B7EA1",  "#6C3302", "#FDB515", "#00B0DA",  "#CFDD45") # berkeley colors

@@

```{r overest}
set.seed(12345)
true <- 3 # sigma_g = 0.15, sigma_m = 0
source("../appendix/pomdp_overestimate.R")
pomdp_overest_sims <- 
  map2_dfr(models, alphas, function(.x, .y){
    pomdp_overestimates(transition = .x$transition, 
            model_observation = .x$observation, 
            reward = .x$reward, 
            discount = discount, 
            true_observation = models[[true]]$observation,
            x0 = x0,
            Tmax = Tmax,
            alpha = .y,
            reps = reps)$df %>% 
              mutate(method = "pomdp") # include a column labeling method
           },
           .id = "scenario"
  )
```

@@
